\myTitle

### 2024-04-24 tex/body-text-of-paper.tex
Adding to the methods

Basic data summaries were calculated for each collection
using simple operations in the R programming language, Version 4.2
\citep{rcore}. We start with a simple tally of the number of alleles
found at each locus.  To provide a summary of the genetic variation and
missing data we report 1) the average over loci of the number of fish
in which each locus was successfully genotyped ($\bar{N}$);
2) the average number of alleles per locus with all collections
downsampled to the smallest number of genotyped individuals at each
locus ($\bar{N}_{A,ss}$);  3) the fraction of polymorphic
loci in each collection after subsampling to the smallest number of genotyped
fish ($\bar{P}_{poly,ss}$); 4) the expected heterozygosity (average over loci
of one minus the frequencies of homozygotes at each locus expected from the
estimated allele frequencies; and 5) the observed heterozygosity (average over
loci of the fraction of heterozygous genotypes.
When subsampling each collection to the minimum number of genotyped
fish across all collections at a locus, we subsampled individuals without
replacement, taking the average of 1,000 different random subsamples.

We calculated \citet{weir1984estimating}'s pairwise $F_\mathrm{ST}$ between
all collections, using the {\footnotesize\tt pp.fst} function from the R
package 'hierfstat' \citep{hierfstat}. Finally, we evaluated population
structure in the data by performing unsupervised clustering of the
the complete data set (\comment{With or without the LFAR? Which did Anthony use?}) 
using the program STRUCTURE \citep{pritchard2000inference,falush2003inference}.
We performed 20 replicate runs at each value of the assumed number of
subpopulations, $K$, in $\{2, 3, 4, 5, 6\}$ 
\comment{I think we should also see what $K=7$ turns up}
using default settings of the program.

@@

>>>>

Basic data summaries were calculated for each collection
using simple operations in the R programming language, Version 4.2
\citep{rcore}. We started with a simple tally of the number of alleles
found at each locus.  To provide a summary of the genetic variation and
missing data we report
\begin {itemize}
\item the average over loci of the number of fish
in which each locus was successfully genotyped, $\bar{N}$;
\item the average number of alleles per locus with all collections
downsampled to the smallest number of genotyped individuals at each
locus, $\bar{N}_\mathrm{A,ss}$,
\item the fraction of polymorphic
loci in each collection after subsampling to the smallest number of genotyped
fish, $\bar{P}_\mathrm{poly,ss}$,
\item the expected heterozygosity as the average over loci
of one minus the frequencies of homozygotes at each locus expected from the
estimated allele frequencies, $\bar{H}_\mathrm{exp}$, and 
\item the observed heterozygosity as the average over
loci of the fraction of heterozygous genotypes, $\bar{H}_\mathrm{obs}$.
\end{itemize}
When subsampling each collection to the minimum number of genotyped
fish across all collections at a locus, we subsampled individuals without
replacement, taking the average of 1,000 different random subsamples.

We calculated \citet{weir1984estimating}'s pairwise $F_\mathrm{ST}$ between
all collections, using the {\footnotesize\tt pp.fst} function from the R
package 'hierfstat' \citep{hierfstat}. Finally, we evaluated population
structure in the data by performing unsupervised clustering of
the complete data set (\comment{With or without the LFAR? Which did Anthony use?}) 
using the program STRUCTURE \citep{pritchard2000inference,falush2003inference}.
We performed 20 replicate runs at each value of the assumed number of
subpopulations, $K$, in $\{2, 3, 4, 5, 6\}$ 
\comment{I think we should also see what $K=7$ turns up}
using default settings of the program.

@@

To assess the power of the marker panel for GSI, we used the R package
'rubias' \citep{moran2019bayesian}.  We used the function {\tt self\_assign()}
to perform assignment of each individual in the reference baseline to one of the
collections within the baseline.  Each fish was removed from the reference baseline
when calculating the likelihood that it originated from the collection it actually belongs
to, using a classical leave-one-out approach to eliminate the inflated estimates of
power that might occur without such a procedure \citep{anderson2008improved}.
The scaled likelihoods of collection membership returned by
{\tt self\_assign()} were summed within reporting units, and fish were
assigned to the reporting unit with the largest value of that sum.  Subsequently,
fish were assigned to the collection within that reporting unit with the highest
scaled likelihood.
